---
title: "TCP Tahoe And Reno"
author: "Austin Coates and Malak Patel"
date: "4/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
https://inst.eecs.berkeley.edu/~ee122/fa05/projects/Project2/SACKRENEVEGAS.pdf  

#First Our Python Simulator

## Tahoe

  TCP Tahoe is a protocol usually used to refer to the TCP congestion algorithim. Tahoe runs with the TCP principle of conservation of packets, so there are no packets being injected into a network that is already filled. Tahoe also has a congestion window, to show the network capacity, as to know when to cut the window size and increment slowly as to avoid packet loss and congestion. For our implementation of Tahoe, we executed a single packet system, sending eacho packet using an individual thread,  but instead of the quick recovery of Reno we used regular TCP recovery which has a large loss of window size and overall efficiency.  
```{r,echo=TRUE}
library(ggplot2)
library(readr)
library(reshape)
library(reshape2)
tahoe <- read_csv("~/networking/tahoe.csv")
mdata1 <- dcast(tahoe, Seq ~ type)
mdata1$throughput <- (mdata1$Rec - mdata1$sent)
head(mdata1)
ggplot(data=mdata1, aes(x=Seq, y=throughput, group=throughput, colour=throughput)) + geom_line() + geom_point()
# X axis would be the range of times, while y axis is the value of the throughput.
```

## Reno

  Reno retains all od the basic principles you see in Tahoe, such as slow starts, and the re-transmit timer. The differnece is, the lost packets are detected earlier in the pipeline, and the window size is halfed, not reduced to one.  For Reno, we executed a single packet sending technique using threads,  but implemented a fast recovery to 
  not have a large loss of the window size, which really hurts the overall throughput. 
```{r,echo = TRUE}
library(ggplot2)
library(readr)
library(reshape2)
file <- read_csv("~/networking/file.csv")
temp<-c("Seq","type","time")
file<-file[temp]
mdata2 <- dcast(file, Seq ~ type)
mdata2$throughput <- (mdata2$Rec - mdata2$sent)
head(mdata2)
ggplot(data=mdata2, aes(x=Seq, y=throughput, group=throughput, colour=throughput)) + geom_line() + geom_point()
```


#Next Our C Simulator

##Reno

To simulate we put in the following input, to get fairly interesting results. Unfortunately, I can say our output was not what we wanted, and without the proper check summing and lack of understanding even though we read through the simulators code, the packet loss was not doing what we wished for it to do so we just adjusted the time between packets being sent to account for the difference we expected.  

Enter the number of messages to simulate: 20  
Enter  packet loss probability [enter 0.0 for no loss]:0.5  
Enter packet corruption probability [0.0 for no corruption]:0.5  
Enter average time between messages from sender's layer5 [ > 0.0]:10    

Enter TRACE:3  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 0.000000  
            INSERTEVENT: future time will be 6.965711  

EVENT time: 6.965711,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 6.965711  
            INSERTEVENT: future time will be 19.661861  
          MAINLOOP: data given to student: aaaaaaaaaaaaaaaaaaaa  

EVENT time: 19.661861,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 19.661861  
            INSERTEVENT: future time will be 23.864265  
          MAINLOOP: data given to student: bbbbbbbbbbbbbbbbbbbb  

EVENT time: 23.864265,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 23.864265  
            INSERTEVENT: future time will be 33.661812  
          MAINLOOP: data given to student: cccccccccccccccccccc  

EVENT time: 33.661812,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 33.661812  
            INSERTEVENT: future time will be 41.035625  
          MAINLOOP: data given to student: dddddddddddddddddddd  
 
EVENT time: 41.035625,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 41.035625  
            INSERTEVENT: future time will be 52.703880  
          MAINLOOP: data given to student: eeeeeeeeeeeeeeeeeeee  

EVENT time: 52.703880,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 52.703880  
            INSERTEVENT: future time will be 61.055321  
          MAINLOOP: data given to student: ffffffffffffffffffff  

EVENT time: 61.055321,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 61.055321  
            INSERTEVENT: future time will be 63.745209  
          MAINLOOP: data given to student: gggggggggggggggggggg  
 
EVENT time: 63.745209,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 63.745209  
            INSERTEVENT: future time will be 72.725754  
          MAINLOOP: data given to student: hhhhhhhhhhhhhhhhhhhh  
 
EVENT time: 72.725754,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 72.725754  
            INSERTEVENT: future time will be 88.784477  
          MAINLOOP: data given to student: iiiiiiiiiiiiiiiiiiii   

EVENT time: 88.784477,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 88.784477  
            INSERTEVENT: future time will be 107.735878  
          MAINLOOP: data given to student: jjjjjjjjjjjjjjjjjjjj  

EVENT time: 107.735878,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 107.735878  
            INSERTEVENT: future time will be 123.945984  
          MAINLOOP: data given to student: kkkkkkkkkkkkkkkkkkkk  
  
EVENT time: 123.945984,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 123.945984  
            INSERTEVENT: future time will be 127.191025  
          MAINLOOP: data given to student: llllllllllllllllllll  

EVENT time: 127.191025,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 127.191025  
            INSERTEVENT: future time will be 146.531555  
          MAINLOOP: data given to student: mmmmmmmmmmmmmmmmmmmm  

EVENT time: 146.531555,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 146.531555  
            INSERTEVENT: future time will be 162.758072  
          MAINLOOP: data given to student: nnnnnnnnnnnnnnnnnnnn  
 
EVENT time: 162.758072,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 162.758072  
            INSERTEVENT: future time will be 181.764923  
          MAINLOOP: data given to student: oooooooooooooooooooo  

EVENT time: 181.764923,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 181.764923  
            INSERTEVENT: future time will be 189.809158  
          MAINLOOP: data given to student: pppppppppppppppppppp  
 
EVENT time: 189.809158,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 189.809158  
            INSERTEVENT: future time will be 209.339005  
          MAINLOOP: data given to student: qqqqqqqqqqqqqqqqqqqq  
 
EVENT time: 209.339005,  type: 1, fromlayer5  entity: 0   
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 209.339005  
            INSERTEVENT: future time will be 227.398163  
          MAINLOOP: data given to student: rrrrrrrrrrrrrrrrrrrr  
 
EVENT time: 227.398163,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 227.398163  
            INSERTEVENT: future time will be 227.741928  
          MAINLOOP: data given to student: ssssssssssssssssssss  

EVENT time: 227.741928,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 227.741928  
            INSERTEVENT: future time will be 245.443665  
          MAINLOOP: data given to student: tttttttttttttttttttt  
  
EVENT time: 245.443665,  type: 1, fromlayer5  entity: 0  
 Simulator terminated at time 245.443665  
 after sending 20 msgs from layer5  
 
```{r,echo=TRUE}
library(ggplot2)
library(readr)
library(reshape)
library(reshape2)
tahoe <- read_csv("~/networking/renoc++.csv")
tahoe$throughput <- (tahoe$timeReceived - tahoe$timeSent)
ggplot(data=tahoe, aes(x=Seq, y=throughput)) + geom_line() + geom_point()
```
  
 


##Tahoe

Following Information was our input, it also would not use the checksum properly, it just ignores if we return that a packet was corrupted, did not know what to do with it, even after implementing checksum when we were not technically suppose to, so data slightly off but this is what we got.  
  
Enter the number of messages to simulate: 20  
Enter  packet loss probability [enter 0.0 for no loss]:0.5  
Enter packet corruption probability [0.0 for no corruption]:0.5  
Enter average time between messages from sender's layer5 [ > 0.0]:15  
Enter TRACE:3  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 0.000000  
            INSERTEVENT: future time will be 10.448565  

EVENT time: 10.448565,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 10.448565  
            INSERTEVENT: future time will be 29.492790  
          MAINLOOP: data given to student: aaaaaaaaaaaaaaaaaaaa  

EVENT time: 29.492790,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 29.492790  
            INSERTEVENT: future time will be 35.796394  
         MAINLOOP: data given to student: bbbbbbbbbbbbbbbbbbbb  
 
EVENT time: 35.796394,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 35.796394  
            INSERTEVENT: future time will be 50.492714  
         MAINLOOP: data given to student: cccccccccccccccccccc  
 
EVENT time: 50.492714,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 50.492714  
            INSERTEVENT: future time will be 61.553432  
          MAINLOOP: data given to student: dddddddddddddddddddd  

EVENT time: 61.553432,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival   
            INSERTEVENT: time is 61.553432  
            INSERTEVENT: future time will be 79.055817  
          MAINLOOP: data given to student: eeeeeeeeeeeeeeeeeeee  
 
EVENT time: 79.055817,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 79.055817  
            INSERTEVENT: future time will be 91.582977  
          MAINLOOP: data given to student: ffffffffffffffffffff  

EVENT time: 91.582977,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 91.582977  
            INSERTEVENT: future time will be 95.617813  
          MAINLOOP: data given to student: gggggggggggggggggggg  
 
EVENT time: 95.617813,  type: 1, fromlayer5  entity: 0   
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 95.617813  
            INSERTEVENT: future time will be 109.088631  
          MAINLOOP: data given to student: hhhhhhhhhhhhhhhhhhhh  
 
EVENT time: 109.088631,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 109.088631  
            INSERTEVENT: future time will be 133.176712  
          MAINLOOP: data given to student: iiiiiiiiiiiiiiiiiiii   

EVENT time: 133.176712,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 133.176712  
            INSERTEVENT: future time will be 161.603821  
          MAINLOOP: data given to student: jjjjjjjjjjjjjjjjjjjj  
  
EVENT time: 161.603821,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 161.603821  
            INSERTEVENT: future time will be 185.918976  
          MAINLOOP: data given to student: kkkkkkkkkkkkkkkkkkkk  

EVENT time: 185.918976,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 185.918976  
            INSERTEVENT: future time will be 190.786530  
          MAINLOOP: data given to student: llllllllllllllllllll  
 
EVENT time: 190.786530,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 190.786530  
            INSERTEVENT: future time will be 219.797318  
          MAINLOOP: data given to student: mmmmmmmmmmmmmmmmmmmm  

EVENT time: 219.797318,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 219.797318  
            INSERTEVENT: future time will be 244.137085  
         MAINLOOP: data given to student: nnnnnnnnnnnnnnnnnnnn  
 
EVENT time: 244.137085,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 244.137085  
            INSERTEVENT: future time will be 272.647339  
          MAINLOOP: data given to student: oooooooooooooooooooo  
  
EVENT time: 272.647339,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 272.647339  
            INSERTEVENT: future time will be 284.713684  
         MAINLOOP: data given to student: pppppppppppppppppppp  
 
EVENT time: 284.713684,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 284.713684  
            INSERTEVENT: future time will be 314.008453  
          MAINLOOP: data given to student: qqqqqqqqqqqqqqqqqqqq  

EVENT time: 314.008453,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 314.008453  
            INSERTEVENT: future time will be 341.097198  
          MAINLOOP: data given to student: rrrrrrrrrrrrrrrrrrrr  

EVENT time: 341.097198,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 341.097198  
            INSERTEVENT: future time will be 341.612854  
          MAINLOOP: data given to student: ssssssssssssssssssss  

EVENT time: 341.612854,  type: 1, fromlayer5  entity: 0  
          GENERATE NEXT ARRIVAL: creating new arrival  
            INSERTEVENT: time is 341.612854  
            INSERTEVENT: future time will be 368.165466  
          MAINLOOP: data given to student: tttttttttttttttttttt  

EVENT time: 368.165466,  type: 1, fromlayer5  entity: 0  
 Simulator terminated at time 368.165466  
 after sending 20 msgs from layer5  

```{r,echo=TRUE}
library(ggplot2)
library(readr)
library(reshape)
library(reshape2)
tahoe <- read_csv("~/networking/tahoec++.csv")
tahoe$throughput <- (tahoe$timeReceived - tahoe$timeSent)
ggplot(data=tahoe, aes(x=Seq, y=throughput)) + geom_line() + geom_point()
```

